---
title: "How to write good code"
author: "Eric Kort"
date: "6/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Programming a computer is a science. Writing maintainable, understandable, 
dependable, and efficient code is an art. The key elements of effective 
coding are:

1. Consistent format
2. Clear but concise documentation
3. Non-repetition
4. Short lines, small functions
5. Organization
6. Unit testing, and test driven development


## Consistent format

The main choices you have for formatting relate to brackets and variable 
names.  There are at least two ways to bracket:

```{r}
a <- function(n) {
  print(n)
}

b <- function(n) 
{
  print(n)
}

a(1)
b(1)

```

I prefer the first way because it is a little more concise. But the second 
way makes it easier to see what bracket level you are at, which is 
helpful if you have lots of nested brackets. Choose either way and stick 
with it.

The second issue is variable names. In R, all the following are options:

```{r}

myVariable <- 1
my_variable <- 2
my.variable <- 3

```
I would stay away from the last one because in several other languages, 
`my.variable` would refer to the method or field `variable` of an object 
called `my`. So do your future self a favor and don't get into the habit 
of using variable names with dots in them.

The first variable is called Camel Case, because the different parts of the 
name are capitalized, giving the variable a camel like appearance. The second 
variable is underscore format. Choose either one and stick with it.

## Clear but consise documentation

It is essential that you document your code. 
Sometimes it is tempting to think "Aack...I'm just going to write a few lines 
of code here to try something out." Before you know it, you have a hundred 
lines of code and nothing is documented. So get into the habit of documenting 
early and often.

There are two ways to document in R. One is to create a document like this 
one that mixes sections of text with section of code. The text provide a long 
form documentation of the code as well as explanations of methods and results.
Unless you are developing a new R package, the best way to go is to always be 
working within an R Markdown document like this one. If your work leads to 
publication, the R Markdown document is also very useful for documenting your 
analysis methods and ensuring that your analysis can be reproduced.

If you are developing an R package because you have some new functionality 
that you want to share with colleagues or the general public, you will need 
to put documentation in your code. Actually, documentation for an R package 
ends up is special R Documentation files. But a tool called roxygen can 
generate those files for you if you document your code in a specific way. 
This way, you don't need to maintain documentation files that are separate 
from your code, and your documentation is right with your code where you need 
it when you are developing. See additional details 
[here](http://r-pkgs.had.c
}

```{r}


```
